---
title: "Problem 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---


```{r setup, include = FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(p8105.datasets)
data("rest_inspec")
```

Column {data-width=700}
-----------------------------------------------------------------------

### Chart A: How many "critical" violations have been amassed per grade?


```{r}
  rest_inspec %>% 
  slice_sample(n = 1000) %>% 
  drop_na(grade) %>% 
  mutate(
      grade = factor(grade, levels = c("A", "B", "C", "Z", "Not Yet Graded"))
  ) %>% 
  group_by(grade, critical_flag) %>%
  filter(
    critical_flag == "Critical"
  ) %>%
  summarize(
    n_obs = n()
  ) %>%
  plot_ly(
    x = ~grade, y = ~n_obs, 
    type = "bar"
  )
  
  
```

Column {data-width=350}
-----------------------------------------------------------------------
### Chart B: Most popular Grade A Restaurants by Cuisine and Borough

```{r eval = FALSE}
  rest_inspec %>% 
  slice_sample(n = 1000) %>% 
  drop_na(grade) %>% 
  mutate(
      grade = factor(grade, levels = c("A", "B", "C", "Z", "Not Yet Graded"))
  ) %>% 
  filter(
    grade == "A"
  ) %>%
  group_by(grade, cuisine_description, boro) %>% 
  summarize(
    n_obs = n()) %>% 
  mutate(
    n_obs_perm = n_obs
  ) %>% 
  ungroup() %>% 
  plot_ly(
    x = ~boro, y = ~n_obs_perm, color = ~cuisine_description,
    type = "scatter", mode = "markers",
    alpha = .5, text = ~dba
  )
```



```{r}
  rest_inspec %>% 
  slice_sample(n = 1000) %>% 
  drop_na(grade) %>% 
  mutate(
      grade = factor(grade, levels = c("A", "B", "C", "Z", "Not Yet Graded"))
  ) %>% 
  filter(
    grade == "A"
  ) %>%
  group_by(grade, cuisine_description, boro) %>% 
  summarize(
    n_obs = n()) %>% 
  mutate(
    n_obs_perm = n_obs
  ) %>% 
  ungroup() %>% 
  plot_ly(
    x = ~boro, y = ~n_obs_perm, color = ~cuisine_description,
    type = "scatter", mode = "markers",
    alpha = .5
  )
```

### Chart C

```{r}

```


However, the website’s _site.yml file conflicts with the dashboard’s YAML header regarding the output format – and the website’s _site.yml “wins”. To address this issue, instead of knitting you can use this command to knit the dashboard.

rmarkdown::render("dashboard_template.Rmd", output_format = "flexdashboard::flex_dashboard")
This will create dashboard_template.html but not open it in RStudio’s Viewer pane; you can open the file in a browser instead. Alternatively, using RStudio’s Build pane to Build Website will produce the same results. To illustrate, we’ll put the dashboard we just created on a website for this topic.

All of this YAML business is only an issue for dashboards embedded in websites; a standalone dashboard (in a non-website GH repo or R Project) can be knit using the same process as other .Rmd files.